### 2015-02-20 fundamentals/impl.tex
for brevity

Multiple strategies, collectively known as \emph{\gls{QA}}, have
been invented to mitigate the structural and algorithmic errors
in software. These include \emph{\gls{VV}}
\cite{boehm_software_1989}, \emph{\gls{UQ}}
\cite{sacks_design_1989}, testing, and others. \gls{VV} and \gls{UQ} come from
a distinctly computational science background while testing \emph{et al.} come from software development.

>>>>

Multiple strategies, collectively known as \emph{\gls{QA}}, have
been invented to mitigate structural and algorithmic errors
in software. These include \emph{\gls{VV}}
\cite{boehm_software_1989}, \emph{\gls{UQ}}
\cite{sacks_design_1989}, testing, and others.
